A Monte Carlo Synthetic Acceleration Method for Solving the Thermal Radiation Diffusion Equation\tnoteref{label1}

### 2012-07-13 doc/jcomp2012/jcomp2012.tex
Adding figure and data file adjoint vs. direct cpu time comparision

\begin{equation}
  \frac{\partial u}{\partial t} = \alpha \nabla^2 u
  \label{eq:poisson_equation}
\end{equation}

where $\alpha$ is a constant coefficient. For all comparisons, a
single time step is computed with backwards Euler time
integration. The Laplacian is differenced on a square Cartesian grid
with a second-order five point stencil

@@

A timing study and convergence study is used to demonstrate the
effectiveness of the adjoint method as compared to the direct
method. To assess both the CPU time and number of iterations required
to converge to a solution, a problem of constant grid size and
$\alpha$ was used with varying values of problem size, fixing the
spectral radius of the system at a constant value for each
variation. Both the five point and nine point stencils were used with
both the direct and adjoint solvers. For each case, 50 histories were
simulated per cycle with a weight cutoff of $1.0E-4$ for the
stochastic solver and a convergence tolerance of $1.0E-8$ for the MCSA
solver. All computations were completed on a 2.66 GHz Intel Core i7
machine with 8 GB 1067 MHz DDR3 memory.

>>>>

\begin{equation}
  \frac{\partial u}{\partial t} = \nabla^2 u
  \label{eq:poisson_equation}
\end{equation}

For all comparisons, a single time step is computed with backwards
Euler time integration. The Laplacian is differenced on a square
Cartesian grid with a second-order five point stencil

@@

A timing study and convergence study is used to demonstrate the
effectiveness of the adjoint method as compared to the direct
method. To assess both the CPU time and number of iterations required
to converge to a solution, a problem of constant grid size and was
used with varying values of problem size, fixing the spectral radius
of the system at a constant value for each variation. Both the five
point and nine point stencils were used with both the direct and
adjoint solvers. For each case, 50 histories were simulated per cycle
with a weight cutoff of $1.0E-4$ for the stochastic solver and a
convergence tolerance of $1.0E-8$ for the MCSA solver. All
computations were completed on a 2.66 GHz Intel Core i7 machine with 8
GB 1067 MHz DDR3 memory.
